Untitled

### 2024-01-31 Evalsims.Rmd
hey

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
Maybe use the two plots of the blocks tomorrow, with RF as less calibration and GAM as mire

```{r}
library(data.table)
library(ggplot2)
out <- rbindlist(lapply(c(1, 1.5, 2, 2.5, 3), function(shape) {
  data <- fread(paste0("results/sims_calibration_1000_rf_5_0.1_", shape, "_0.6.csv"))
  data$shape <- shape
  data
}))

@@

plt1 <- ggplot(out[out$bin == "marginal"], aes(x = shape_error, y = width, color = method)) + geom_point(aes(shape = method), size = 4)   + theme_bw() + labs(x = TeX("Calibration error in f( )"), y = "Interval Width") +   guides(color = guide_legend(title = element_blank()), shape = guide_legend(title = element_blank())) + 
 theme(legend.text = element_text(size = 11), legend.key.size = unit(2, "lines"))

@@

plt2 <- ggplot(out[out$bin == "marginal"], aes(x = shape, y = coverage, color = method)) + geom_point(aes(shape = method), size = 3)   + theme_bw() + labs(x = TeX("Calibration error in f()"),  y = TeX("Coverage ($\\alpha = 0.1$)")) +   guides(color = guide_legend(title = element_blank()), shape = guide_legend(title = element_blank())) + 
 theme(legend.text = element_text(size = 11), legend.key.size = unit(2, "lines"))

plt2

#combined_plot <- plt1 + plt2 + plot_layout(guides = "collect") & theme(legend.position = "bottom")

#ggsave("plots/calibration_shift.pdf" , width = 7, height = 5)

@@

plot1 <- plot1 + ggtitle("d=5")
plot3 <- plot3 + ggtitle("d=20")
plot5 <- plot5 + ggtitle("Adverserial (d=5)")
combined_plot <- plot1 + plot2+ plot3+ plot4 + plot5 + plot6+ plot_layout(ncol =2, guides = "collect", axis_titles ="collect") & theme(legend.position = "bottom")

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Experiment 1: SC-CP
```{r}
library(data.table)
library(ggplot2)
library(latex2exp)
out <- rbindlist(lapply(c(1, 1.5, 2, 2.5, 3), function(shape) {
  data <- fread(paste0("results/sims_calibration_1000_rf_5_0.1_", shape, "_0.6.csv"))
  data$shape <- shape
  data
}))

@@

plt1 <- ggplot(out[out$bin == "marginal"], aes(x = shape_error, y = width, color = method)) + geom_point(aes(shape = method), size = 4)   + theme_bw() + labs(x = TeX("Calibration error in f( )"), y = "Interval Width ($\\alpha = 0.1$)") +   guides(color = guide_legend(title = element_blank()), shape = guide_legend(title = element_blank())) + 
 theme(legend.text = element_text(size = 11), legend.key.size = unit(2, "lines"))

@@

## Experiment 2: calibration for scoring function
```{r}
library(latex2exp)

results_1 <- rbindlist(readRDS("results/calerror_1.rds"))
results_1 <- results_1[, .(width = mean(width), cal_error = mean(cal_error)), by = c("shape", "alpha", "Status")]
results_1 <- results_1[, .(relative = width[Status=="Calibrated"] / width[Status=="Uncalibrated"]) , by = c("cal_error", "alpha")]

results_2 <- readRDS("results/calerror_2.rds")
results_2 <- results_2[, .(width = mean(width)), by = c("n", "alpha", "Status")]
results_2 <- results_2[, .(relative = width[Status=="Calibrated"] / width[Status=="Uncalibrated"]) , by = c("n", "alpha")]

results_1$alpha <- factor(results_1$alpha, levels = c(0.05, 0.1, 0.2))
results_2$alpha <- factor(results_2$alpha, levels = c(0.05, 0.1, 0.2))

library(latex2exp)

plt1 <- ggplot(results_1 , aes(x = cal_error, y = relative, color = (alpha), linetype = (alpha))) + geom_line() +
  theme_bw() + labs(y = TeX("Relative Width (cal/uncal)"), x = TeX("Calibration error of f ($\\n_{Cal} = 1000)"),
                    color = "Sig. Level", linetype = "Sig. Level") +
  geom_hline(yintercept = 1, color = "black", linetype = "dashed" , alpha = 0.5) + scale_y_continuous(limits = c(0.7, 1.2))

plt2 <- ggplot(results_2 , aes(x = n, y = relative, color = (alpha), linetype = (alpha))) + geom_line() +
  theme_bw() + labs(y = TeX("Relative Width (cal/uncal)"), x = TeX("Calibration set size ($kappa_{train} = 3$)"), color = "Sig. Level", linetype = "Sig. Level") + scale_x_log10() +
  geom_hline(yintercept = 1, color = "black", linetype = "dashed" , alpha = 0.5) + scale_y_continuous(limits = c(0.7, 1.2))

library(patchwork)
combined_plot <- (plt1 + plt2)  + plot_layout(guides = "collect", axis_titles = "collect", axes = "collect") & theme(legend.position = "bottom") #+  labs(color = TeX("$\\alpha$"), linetype = TeX("$\\alpha$"))
combined_plot
print(combined_plot)

ggsave("plots/calibration_shift_2.pdf", plot = combined_plot, width = 6, height = 4)
# this plot is good

@@

plot1 <- plot1 + ggtitle("Setup A (d=5)")
plot3 <- plot3 + ggtitle("Setup B (d=20)")
plot5 <- plot5 + ggtitle("Setup C (adverserial, d=5)")
combined_plot <- plot1 + plot2+ plot3+ plot4 + plot5 + plot6+ plot_layout(ncol =2, guides = "collect", axis_titles ="collect") & theme(legend.position = "bottom")

### 2024-01-31 plot_curves.Rmd
hey

preds_oracle <- data.table(X = as.vector(data_test$X),
                           f = data_test$mu, 
                           lower = qnorm(0.05, data_test$mu, data_test$sigma2),
                           upper = qnorm(0.95, data_test$mu, data_test$sigma2),
                           method = "Oracle")

@@

appender <- function(string) {
    TeX(paste("$n_{cal} = $", string)) 
}

plt <- ggplot(data, aes(x = X, color = method, linetype = method)) +
  geom_step(aes(y = lower), size = 0.8)  +
  geom_step(aes(y = upper), size = 0.8) +
  geom_line(data = preds_oracle, aes(x = X, y = lower), color = "black", alpha = 1, linetype = "solid")  +
  geom_line(data = preds_oracle, aes(x = X, y = upper), color = "black", alpha = 1, linetype = "solid") +
  theme(legend.position="bottom") + theme_bw() + labs(x = "Covariate (X)", color = "", y = "Outcome (Y)") + facet_wrap(~ n, labeller = as_labeller(appender, 
                            default = label_parsed) ) +  labs(color  = "", linetype = "", shape = "")   + theme(legend.key.size = unit(1, "cm"), 
        legend.text = element_text(size = 12),  # Adjust text size here
        legend.title = element_text(size = 14), # Adjust title size here
        legend.position = "bottom", 
        legend.direction = "horizontal",
        legend.margin = margin(0,0,0,0),
        legend.box.margin = margin(-10,-10,-10,-10)) +
  scale_linetype_manual(values = c("solid", "dotted", "dashed", "dotdash"))

>>>>

preds_oracle <- data.table(X = as.vector(data_test$X),
                           f = data_test$mu, 
                           lower = qnorm(0.05, data_test$mu, data_test$sigma),
                           upper = qnorm(0.95, data_test$mu, data_test$sigma),
                           method = "Oracle")

@@

appender <- function(string) {
    TeX(paste("$n_{cal} = $", string)) 
}
preds_oracle <- rbindlist(lapply(sort(unique(data$n)), function(n) {
  dat <- copy(preds_oracle)
  dat$n <- n
  dat
}))
data_all <- rbind(data[, c("n", "X", "f", "lower", "upper", "method"), with = FALSE], preds_oracle)
plt <- ggplot(data_all, aes(x = X, color = method, linetype = method)) +
  geom_step(aes(y = lower), size = 0.8)  +
  geom_step(aes(y = upper), size = 0.8) +
 # geom_line(data = preds_oracle, aes(x = X, y = lower), color = "black", alpha = 1, linetype = "solid")  +
#  geom_line(data = preds_oracle, aes(x = X, y = upper), color = "black", alpha = 1, linetype = "solid") +
  theme(legend.position="bottom") + theme_bw() + labs(x = "Covariate (X)", color = "", y = "Outcome (Y)") + facet_wrap(~ n, labeller = as_labeller(appender, 
                            default = label_parsed) ) +  labs(color  = "", linetype = "", shape = "")   + theme(legend.key.size = unit(1, "cm"), 
        legend.text = element_text(size = 12),  # Adjust text size here
        legend.title = element_text(size = 14), # Adjust title size here
        legend.position = "bottom", 
        legend.direction = "horizontal",
        legend.margin = margin(0,0,0,0),
        legend.box.margin = margin(-10,-10,-10,-10)) +
  scale_linetype_manual(values = c("solid", "dotted", "dashed", "dotdash"))
